Visualizations for the manuscript

### 2022-04-04 metanalysis_visualization/manuscript_Figures.Rmd
roll back to previous forest plot by siteid label. change axis of plots to have all the months

```{r}
outputDir <- "../../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = "../public-data/country_mapping.txt")
```

@@

```{r}
df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid") %>% 
  left_join(country_map, by = "siteid")

names_site_id <- unique(df_coefficients_boot$plotsLabel)

plot_annotations <- df_coefficients_boot %>% 
  group_by(plotsLabel) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  plotsLabel = names(plot_annotations), 
  label = plot_annotations
)
```

@@

```{r}
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

@@

```{r}
trends_siteid <- df_coefficients_boot %>% 
  group_by(plotsLabel) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
            observed = unique(observed_diff),
            var_boot = var(`periodduring_pandemic:time`), 
            z = mean_boot / sqrt(var_boot), 
            pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

@@

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
```

```{r}
trends_country <- trends_siteid %>% 
  group_by(plotsLabel) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

@@

forest(model_meta_country, 
       slab = trends_country$plotsLabel,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```

@@

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  # geom_label(data = plot_annotations_sex_df[["male"]],
  #            aes(label=label),
  #            x = -Inf,
  #            y = 15,
  #            hjust = 0,
  #            vjust = 0,
  #            size = 4,
  #           inherit.aes = FALSE) +
  # ylim(10, 90) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
```
### Disorder group fix

>>>>

```{r}
outputDir <- "../../output/previous_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = "../public-data/country_mapping.txt")
```

@@

```{r}
df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid")
names_site_id <- unique(df_coefficients_boot$siteid)
plot_annotations <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)
```

@@

```{r}
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 45, units = "cm")
```

@@

```{r}
trends_siteid <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
            observed = unique(observed_diff),
            var_boot = var(`periodduring_pandemic:time`), 
            z = mean_boot / sqrt(var_boot), 
            pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

@@

metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
```

```{r}
trends_country <- trends_siteid %>% 
  left_join(country_map, by = "siteid") %>% 
  group_by(country) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

@@

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```

@@

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  # geom_label(data = plot_annotations_sex_df[["male"]],
  #            aes(label=label),
  #            x = -Inf,
  #            y = 15,
  #            hjust = 0,
  #            vjust = 0,
  #            size = 4,
  #           inherit.aes = FALSE) +
  # ylim(10, 90) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
```
### Disorder group fix
